Survey of Cache Oblivious B-trees

### 2011-12-12 paper.tex
Adding conclusion

@@

\section{Conclusion}
Fill this in.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
Fill this in.

>>>>

\begin{figure*}[h!t]
\begin{center}
    \begin{tabular}{ |   l   |  l     |     l     |     }
    \hline
	Data Structure & Search & Insert / Delete  \\ \hline \hline
	 \textit{Original CO B-tree}  & $O(\log_{B}{N})$ & $O(\log_{B}{N} + \frac{\log^2{N}}{B})$  \\ \hline
	\textit{String CO B-tree}  & $O(1+\log_{B}N+||k||/B)$ &   $O(1+\log_{B}N+\log^{2}N||k||/B)$  \\ \hline
	\textit{Streaming Shuttle Tree}  & $O(\log_{B}{N})$ &  $O(log_{B+1} N / B^{\Theta(1/(loglogB)^2)} + (log^2 N) / B)$  \\ \hline
	\textit{Streaming COLA}  & $O(\log N)$ & $O((\log N) / B)$  \\ \hline
	\textit{Concurrent Exponential CO B-tree} &   $O(\log_B{N} + \log_{\alpha}{\log{B}})$  &   $O(\log_B{N} + \log{\alpha}{\log{B}})$  \\ \hline
	\textit{Concurrent PMA CO B-tree}  & $O(\log_{B}{N} + ({\log{N}})/{B} + 1)$ &   $O(\log_{B}{N} + (\log^2{N})/{B} + 1)$  \\ \hline
    \end{tabular}
    \caption{A summary of the surveyed CO B-trees. The bounds are in terms of the number of memory transfers. The bounds for \textit{Concurrent Exponential CO B-tree} are in expectation only.}
    \label{fig:table}
\end{center}
\end{figure*}

@@

\section{Conclusion}

This paper presented a survey on different types of cache-oblivious B-trees: the 
original \textit{cache-oblivious B-tree}, the \textit{cache-oblivious string
B-tree}, the \textit{cache-oblivious streaming B-tree}, and the \textit{cache-oblivious
concurrent B-tree}. A summary of these data structures is provided
in Figure~\ref{fig:table}.

\section{Acknowledgments}
We sincerely thank Dr. David Karger and all of the TAs for 6.854 
for their guidance, help, and support. May the Flow (Max-Flow, that is) be with you all.
